The Astropy Project: xx

### 2021-11-16 src/ms.tex
add outline of paper from google doc

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Style notes:
%
%   -
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{The Astropy Project: xx and status of the v5.0 core package}

@@

\section{Placeholder} \label{sec:placeholder}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   Please read the CONTRIBUTING.md file in this repository for notes about
%   style and latex conventions!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{The Astropy Project: xx}

@@

\section{Major Updates in the Astropy Project} \label{sec:project-updates}

\subsection{Project governance} \label{sec:project-governance}

New CoCo and election overview.

\subsection{Contributor base} \label{sec:project-contributors}

Overview and statistics of contributors. Changes since v2.0.

@@

\subsection{Funding} \label{sec:project-funding}

New funding sources.

\section{Major Updates to the Astropy Core Package} \label{sec:core-updates}

\subsection{New Long-term Support (LTS) Version: v5.0} \label{sec:core-v50}

\subsection{Highlighted Feature Development} \label{sec:core-features}

Timeseries, Box Least Squares

TODO: go through What's New pages and identify a few big additions / changes.

\section{Learn Astropy} \label{sec:learn}

Current status and scope

Vision for the future (review what we said in v2.0 paper)

User forums and engagement with user base

\section{Supporting the Ecosystem of Astronomical Python Software}
\label{sec:ecosystem}

\subsection{Community-oriented infrastructure}

Infrastructure packages that exist to support and help others maintain their package infrastructure.

\subsection{Affiliated packages}

Updates!

\subsection{Connections with observatories}

JWST (motivated by excitement around the launch?)

Gemini

\section{Future Plans for the Astropy Project} \label{sec:future}

\subsection{Roadmap}

\subsection{Challenges}

Attracting new contributors when the code has become quite complex,
Contributor to maintainer mentoring,
Long-term / sustained funding for maintaining infrastructure,
...
